Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Move functions to R/. Constrain fig 1 y axis

```{r}
#| label: setup
#| include: false  
library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(patchwork)

@@

format_signif <- function(x, digits) {
  formatC(signif(x, digits = digits), digits = digits, format = "fg", flag = "#")
}
format_pval <- function(p, digits) {
  ifelse(p < 10^-digits,
         sprintf("<%s", format(10^-digits, digits = 1, scientific = FALSE)),
         sprintf(paste0("%0.", digits, "f"), p))
}

@@

breed_nonbreed <- sealdat %>% 
  group_by(age) %>% 
  summarize(n_observed = sum(!is.na(observed)), 
            perc_breed = sum(observed == "Breeder") / n_observed, 
            se = (perc_breed * (1 - perc_breed) / n_observed)^0.5) %>% 
  filter(age < 22) %>%
  ggplot(aes(x = age, y = perc_breed)) + 
  geom_ribbon(aes(x, ymin = conf.low, ymax = conf.high),
              breed_pred,
              inherit.aes = FALSE,
              fill = "#829BD1",
              alpha = 0.25) +
  geom_line(aes(x, predicted),
            breed_pred,
            inherit.aes = FALSE,
            color = "#829BD1",
            linewidth = 1) +
  geom_point() + 
  geom_errorbar(aes(ymin = perc_breed - se, ymax = perc_breed + se), width = 0) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) + 
  labs(x = "Maternal Age (Years)", y = "% Breeders (Mean ± SE)") + 
  theme_few() + 
  theme(axis.title = element_text(size = 13))

>>>>

```{r}
#| label: setup
#| include: false  
library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(patchwork)
source(here::here("R/format.R"))

@@

@@

breed_nonbreed <- sealdat %>% 
  group_by(age) %>% 
  summarize(n_observed = sum(!is.na(observed)), 
            perc_breed = sum(observed == "Breeder") / n_observed, 
            se = (perc_breed * (1 - perc_breed) / n_observed)^0.5) %>% 
  filter(age < 22) %>%
  ggplot(aes(x = age, y = perc_breed)) + 
  geom_ribbon(aes(x, ymin = conf.low, ymax = conf.high),
              breed_pred,
              inherit.aes = FALSE,
              fill = "#829BD1",
              alpha = 0.25) +
  geom_line(aes(x, predicted),
            breed_pred,
            inherit.aes = FALSE,
            color = "#829BD1",
            linewidth = 1) +
  geom_point() + 
  geom_errorbar(aes(ymin = perc_breed - se, ymax = perc_breed + se), width = 0) +
  scale_y_continuous(labels = scales::percent, limits = c(0.5, 1)) + 
  labs(x = "Maternal Age (Years)", y = "% Breeders (Mean ± SE)") + 
  theme_few() + 
  theme(axis.title = element_text(size = 13))
